---
title: Blog Post 1
author: Yusuf Mian
date: '2022-09-09'
slug: []
categories: []
tags: []
---


```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE, eval=TRUE, fig.align="center"}
knitr::opts_chunk$set(echo = FALSE)
library(ggplot2)
library(tidyverse)
#### want a state-level analysis
library(readr)
setwd("~/Desktop/Election Analysis/Election-Blog")
popvote_df <- read_csv("house nationwide vote and seat share by party 1948-2020.csv")
house_party_vote_share_by_district_1948_2020 <- read_csv("house party vote share by district 1948-2020.csv")
h <- house_party_vote_share_by_district_1948_2020
```


## Geographic and temporal trends in midterm elections?

In this weekly blog series, I will be analyzing and predicting the 2022 midterms as we approach the November election. This first blog post will be exploring trends in elections by looking at the congressional elections in the State of Michigan to explore a key swingtate, which voted for Trump in 2016 and Biden in 2020. I also will be exploring some of the recent trends of popular voteshare by state and congressional district in recent elections.

```{r, include=TRUE, message=FALSE, warning=FALSE, echo=FALSE, eval=TRUE, fig.align="center"}
## make map of vote share by state and CD

# start with 114th congress - 2014 election
# required packages 
require(tidyverse)
require(ggplot2)
require(sf)
library(plotly)

# load geographic data
get_congress_map <- function(cong=117) {
  tmp_file <- tempfile()
  tmp_dir  <- tempdir()
  zp <- sprintf("https://cdmaps.polisci.ucla.edu/shp/districts114.zip",cong)
  download.file(zp, tmp_file)
  unzip(zipfile = tmp_file, exdir = tmp_dir)
  fpath <- paste(tmp_dir, sprintf("districtShapes/districts114.shp",cong), sep = "/")
  st_read(fpath)
}

# load 114th congress
cd117 <- get_congress_map(117)

# select specific state 
cd117_mi <- cd117 %>% 
            filter(STATENAME=="Michigan") %>%
            mutate(DISTRICT = as.character(DISTRICT))%>%
            select(DISTRICT)

# add data to plot - 2014 GOP party seat share
# reload election data - h from previous exercise
h <- house_party_vote_share_by_district_1948_2020

# filter for 2014 election and state
R_mi_2020 <- h %>%
    filter(raceYear == 2020, State == "Michigan") %>%
    select(raceYear, State, district_num, RepVotesMajorPercent, DemVotesMajorPercent) %>%
  # summarize party vote share by district
    group_by(district_num) %>%
    summarise(Rep_votes_pct = RepVotesMajorPercent) %>%
  # rename district variable name to match shapefile
    rename(DISTRICT = district_num)

# before joining dfs, check classes of variable to be merged on
class(R_mi_2020$DISTRICT)
class(cd117_mi$DISTRICT)

# change class
cd117_mi$DISTRICT <- as.numeric(cd117_mi$DISTRICT)

# join election returns with shapefiles
cd117_mi <- cd117_mi %>% left_join(R_mi_2020, by="DISTRICT")
cd117_mi

# time to map!
mimap <- ggplot() + 
  geom_sf(data=cd117_mi,aes(fill=Rep_votes_pct),
          inherit.aes=FALSE,alpha=0.9) + 
  scale_fill_gradient(low = "white", high = "black", limits=c(10,80)) +
  theme_void() + ggtitle ("Republican Vote Share in 2020 MI Congressional Elections")
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank(),
        axis.title.y=element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank()) + ggthemes::theme_fivethirtyeight() + theme (plot.background= element_rect(color="blue"))
  
fig <- ggplotly(mimap)
fig


## make map of GOP vote share by state (national) - 2014
# use h dataset from earlier
# house_party_vote_share_by_district_1948_2020 <- 
  # read_csv("house party vote share by district 1948-2020.csv")
# h <- house_party_vote_share_by_district_1948_2020
 
# filter for relevant variables
R_2020 <- h %>%
    filter(raceYear == 2020) %>%
    select(raceYear, State, district_num, district_id, RepVotes, DemVotes) %>%
  # summarize party vote share by state
    group_by(State) %>%
  # mutate Rep vote margin by state %>%
    mutate(R_votemargin_st = (sum(RepVotes))/
                            sum(RepVotes + DemVotes),
           D_votemargin_st = (sum(DemVotes))/
                            sum(RepVotes + DemVotes)) %>%
    rename(state = State)
R_2014 <- h %>%
    filter(raceYear == 2014) %>%
    select(raceYear, State, district_num, district_id, RepVotes, DemVotes) %>%
  # summarize party vote share by state
    group_by(State) %>%
  # mutate Rep vote margin by state %>%
    mutate(R_votemargin_st2 = (sum(RepVotes))/
                            sum(RepVotes + DemVotes),
           D_votemargin_st2 = (sum(DemVotes))/
                            sum(RepVotes + DemVotes)) %>%
    rename(state = State)

# load usmap
# install.packages('plot_usmap')
library(usmap)

states_map <- usmap::us_map()
unique(states_map$abbr)

# plot
plot_usmap(data = R_2020, regions = "states", labels=TRUE, values = "R_votemargin_st") + 
  scale_fill_gradient(low = "white", high = "red", name = "GOP two-party voteshare margin") +
  theme_void() +labs(title="Republican Popular Vote Share in 2020 US House Elections")
plot_usmap(data = R_2014, regions = c("states", "state", "counties", "county"), labels = TRUE, values = "D_votemargin_st2") + 
  scale_fill_gradient(low = "white", high = "blue", name = "Dem two-party voteshare margin") +
  theme_void() +labs(title="Democratic Popular Vote Share by Countyin 2014 US House Elections")
```
