---
title: Blog Post 7
author: Yusuf Mian
date: '2022-10-26'
slug: []
categories: []
tags: []
---
## Shocks
<br>
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
setwd("/Users/yusufmian/Desktop/Election Analysis/Election-Blog")
library(tidyverse); library(knitr)
polls2022 <- read.csv("538_house_polls_2022.csv")
pvi <- read.csv("PVI_share.csv")
house_party_vote_share_by_district_1948_2020 <- read.csv("house party vote share by district 1948-2020.csv")
h <- house_party_vote_share_by_district_1948_2020
cvap_district <- read_csv("cvap_district_2012-2020_clean.csv")
polls_df <- read_csv("house_polls_long.csv")
expert_ratings <- read.csv("expert_rating.csv")
ad_creative  <- read_csv("ads_2006_2018 (1).csv")
library(tidyverse)
library(stargazer)
rdi_df <- read.csv("rdi_quarterly.csv")
gdp_df <- read.csv("GDP_quarterly.csv")
housevoteshare <- read.csv("house_popvote_seats.csv")
econdata <- left_join ( housevoteshare, gdp_df, by="year")

```

```{r}
h2<- h %>% 
  filter(raceYear==2020 | raceYear==2018) %>% 
  rename(year=raceYear)
polls_dfModel <- polls_df %>% 
  mutate(year = ifelse(year%%2!=0, year+1, year)) %>% 
  filter(year!=2022) %>% 
  mutate(cd_fips= as.numeric(cd_fips), st_fips=as.numeric(st_fips), DEM=as.numeric(DEM)) %>% 
  rename(district_num=cd_fips)
pollShare <- full_join(polls_dfModel, h2, by=c("year", "st_fips", "district_num"))
districtpollLM <- lm(DemVotesMajorPercent ~ DEM, data=pollShare)
h2022 <- h %>% 
  filter(raceYear==2022) %>% 
  rename(year=raceYear)
polls2022Dem <- polls2022 %>% 
  filter(party=="DEM") %>% 
  rename(DEM=pct)
polls2022Michigan <- polls2022Dem %>% 
  filter(st_fips==26 & cd_fips==10)
mi10pollingprediction <-mean(predict(districtpollLM, polls2022Michigan))
expert_ratingsModel <- expert_ratings %>% 
  filter(year!=2022) %>% 
  mutate(district=as.numeric(district))
h3 <- h %>% 
  filter(raceYear>=2010) %>% 
  rename(year=raceYear, state=State, district=district_num)
expertShare <- full_join(expert_ratingsModel, h3, by=c("year", "state", "district"))
districtexpertLM <- lm(DemVotesMajorPercent~avg_rating, data=expertShare)
```
## Updates to model
This week, there are no new signifcant updates to the model. However, I have gone and used the district model which I showed in detail last week and used it for all of the districts that should be close and of interest. In the table below, you can see the list of predicted winners and Democratic 2-Party voteshare for these close districts. The weights and formula is the same as the MI-10 I showed last week where Cook PVI of a district is 0.3, the expert prediction model is 0.3, the polling is 0.2, and the economic model is 0.2 However, even though our model is already not great for district polling, it is made even worse in that some districts either had no polling (or the only polling seemed very bad to me because it wasn't even polling the actual nominee or was very old). In these cases, I had to drop polling and chose to add this weight to the expert predictions, which I have found to be the best of our models, so expert predictions becomes 0.5 in that case. One other thing of interest is that I have noticed in some districts which have a PVI indicating a not so close race, Democratic incumbents might be hurt by this in my model. In other words, some Democratic incumbents may be able to win in Trump or Republican districts, but my model doesn't really account for that when considering PVI. Therefore, I am acknowleding this as one possible drawback which I haven't been able to avoid. I still think on the whole PVI is important to consider the landscape of a district and account for voters who vote the same year to year.
<br>
```{r}
mi10expert <- expert_ratings %>% 
  filter(year==2022 & state=="Michigan" & district==10) %>% 
  select(avg_rating)
mi10expertPrediction <- predict(districtexpertLM, mi10expert)
pviMichigan <- pvi %>% 
  filter(District=="Michigan 10")
pvilm <- 50+((pviMichigan$PVI_num)/2)
econ <- econdata %>% 
  filter(year%%4!=0, quarter_cycle=="5")
lm_gdp <- lm(H_incumbent_party_majorvote_pct ~ GDPC1, data=econ)
gdpVotenew <-gdp_df %>% 
  filter(year==2022, quarter_cycle=="5") %>% 
  select(GDPC1)
gdpPrediction <- predict(lm_gdp, gdpVotenew)
expertRsquared <- summary(districtexpertLM)$r.squared
gdpRsquared<- summary(lm_gdp)$r.squared
mi10Prediction <- mean((0.3*pvilm) + (0.3* mi10expertPrediction) + (0.2*mi10pollingprediction) +0.2*(gdpPrediction))
tx15expert <- expert_ratings %>% 
  filter(year==2022 & state=="Texas" & district==15) %>% 
  select(avg_rating)
tx15expertPrediction <- predict(districtexpertLM, tx15expert)
pviTexas15 <- pvi %>% 
  filter(District=="Texas 15")
pvilmTx15 <- 50+((pviTexas15$PVI_num)/2)
polls2022Texas15 <- polls2022Dem %>% 
  filter(st_fips==48 & cd_fips==15)
tx15pollingprediction <-mean(predict(districtpollLM, polls2022Texas15))
tx15Prediction <- mean((0.3*pvilmTx15) + (0.5* tx15expertPrediction) +(0.2*gdpPrediction))
pa7expert <- expert_ratings %>% 
  filter(year==2022 & state=="Pennsylvania" & district==7) %>% 
  select(avg_rating)
pa7expertPrediction <- predict(districtexpertLM, pa7expert)
pviPennsylvania7 <- pvi %>% 
  filter(District=="Pennsylvania 7")
pvilmPa7 <- 50+((pviPennsylvania7$PVI_num)/2)
polls2022Pennsylvania <- polls2022Dem %>% 
  filter(st_fips==42 & cd_fips==7)
pa7pollingprediction <-mean(predict(districtpollLM, polls2022Pennsylvania))
pa7Prediction <- mean((0.3*pvilmPa7) + (0.5* pa7expertPrediction) +  (0.2*gdpPrediction))
ca27expert <- expert_ratings %>% 
  filter(year==2022 & state=="California" & district==27) %>% 
  select(avg_rating)
ca27expertPrediction <- predict(districtexpertLM, ca27expert)
pviCalifornia27 <- pvi %>% 
  filter(District=="California 27")
pvilmca27 <- 50+((pviCalifornia27$PVI_num)/2)
polls2022California27 <- polls2022Dem %>% 
  filter(st_fips==6 & cd_fips==27)
ca27pollingprediction <-mean(predict(districtpollLM, polls2022California27))
ca27Prediction <-mean((0.3*pvilmca27) + (0.3* ca27expertPrediction) + (0.2*ca27pollingprediction) +(0.2*gdpPrediction))
ca22expert <- expert_ratings %>% 
  filter(year==2022 & state=="California" & district==22) %>% 
  select(avg_rating)
ca22expertPrediction <- predict(districtexpertLM, ca22expert)
pviCalifornia22 <- pvi %>% 
  filter(District=="California 22")
pvilmca22 <- 50+((pviCalifornia27$PVI_num)/2)
polls2022California22 <- polls2022Dem %>% 
  filter(st_fips==6 & cd_fips==22)
ca22pollingprediction <-mean(predict(districtpollLM, polls2022California22))
ca22Prediction <-mean((0.3*pvilmca22) + (0.3* ca22expertPrediction) + (0.2*ca22pollingprediction) +(0.2*gdpPrediction))
va2expert <- expert_ratings %>% 
  filter(year==2022 & state=="Virginia" & district==2) %>% 
  select(avg_rating)
va2expertPrediction <- predict(districtexpertLM, va2expert)
pviVirginia2 <- pvi %>% 
  filter(District=="Virginia 2")
pvilmva2 <- 50+((pviVirginia2$PVI_num)/2)
polls2022Virginia2 <- polls2022Dem %>% 
  filter(st_fips==51 & cd_fips==2)
va2pollingprediction <-mean(predict(districtpollLM, polls2022Virginia2))
va2Prediction <-mean((0.3*pvilmva2) + (0.3* va2expertPrediction) + (0.2*va2pollingprediction) +(0.2*gdpPrediction))
az2expert <- expert_ratings %>% 
  filter(year==2022 & state=="Arizona" & district==2) %>% 
  select(avg_rating)
az2expertPrediction <- predict(districtexpertLM, az2expert)
pviArizona2 <- pvi %>% 
  filter(District=="Arizona 2")
pvilmaz2 <- 50+((pviArizona2$PVI_num)/2)
polls2022Arizona2 <- polls2022Dem %>% 
  filter(st_fips==4 & cd_fips==2)
az2pollingprediction <-mean(predict(districtpollLM, polls2022Arizona2))
az2Prediction <-mean((0.3*pvilmaz2) + (0.5* az2expertPrediction) + (0.2*gdpPrediction))

```
```{r}
ks3expert <- expert_ratings %>% 
  filter(year==2022 & state=="Kansas" & district==3) %>% 
  select(avg_rating)
ks3expertPrediction <- predict(districtexpertLM, ks3expert)
pviKansas3 <- pvi %>% 
  filter(District=="Kansas 3")
pvilmks3 <- 50+((pviKansas3$PVI_num)/2)
polls2022Kansas3 <- polls2022Dem %>% 
  filter(st_fips==20 & cd_fips==3)
ks3pollingprediction <-mean(predict(districtpollLM, polls2022Kansas3))
ks3Prediction <-mean((0.3*pvilmks3) + (0.3* ks3expertPrediction) + (0.2*ks3pollingprediction) +(0.2*gdpPrediction))
or5expert <- expert_ratings %>% 
  filter(year==2022 & state=="Oregon" & district==5) %>% 
  select(avg_rating)
or5expertPrediction <- predict(districtexpertLM, or5expert)
pviOregon5 <- pvi %>% 
  filter(District=="Oregon 5")
pvilmor5 <- 50+((pviOregon5$PVI_num)/2)
polls2022Oregon5 <- polls2022Dem %>% 
  filter(st_fips==41 & cd_fips==5)
or5pollingprediction <-mean(predict(districtpollLM, polls2022Oregon5))
or5Prediction <-mean((0.3*pvilmor5) + (0.3* or5expertPrediction) + (0.2*or5pollingprediction) +(0.2*gdpPrediction))

ia3expert <- expert_ratings %>% 
  filter(year==2022 & state=="Iowa" & district==3) %>% 
  select(avg_rating)
ia3expertPrediction <- predict(districtexpertLM, ia3expert)
pviIowa3 <- pvi %>% 
  filter(District=="Iowa 3")
pvilmia3 <- 50+((pviIowa3$PVI_num)/2)
polls2022Iowa3 <- polls2022Dem %>% 
  filter(st_fips==19 & cd_fips==3)
ia3pollingprediction <-mean(predict(districtpollLM, polls2022Iowa3))
ia3Prediction <-mean((0.3*pvilmia3) + (0.3* ia3expertPrediction) + (0.2*ia3pollingprediction) +(0.2*gdpPrediction))

ny19expert <- expert_ratings %>% 
  filter(year==2022 & state=="New York" & district==19) %>% 
  select(avg_rating)
ny19expertPrediction <- predict(districtexpertLM, ny19expert)
pviNY19 <- pvi %>% 
  filter(District=="New York 19")
pvilmny19 <- 50+((pviNY19$PVI_num)/2)
polls2022NY19 <- polls2022Dem %>% 
  filter(st_fips==36 & cd_fips==19)
ny19pollingprediction <-mean(predict(districtpollLM, polls2022NY19))
ny19Prediction <-mean((0.3*pvilmny19) + (0.3* ny19expertPrediction) + (0.2*ny19pollingprediction) +(0.2*gdpPrediction))

ri2expert <- expert_ratings %>% 
  filter(year==2022 & state=="Rhode Island" & district==2) %>% 
  select(avg_rating)
ri2expertPrediction <- predict(districtexpertLM, ri2expert)
pviri2 <- pvi %>% 
  filter(District=="Rhode Island 2")
pvilmri2 <- 50+((pviri2$PVI_num)/2)
polls2022RI2 <- polls2022Dem %>% 
  filter(st_fips==44 & cd_fips==2)
ri2pollingprediction <-mean(predict(districtpollLM, polls2022RI2))
ri2Prediction <-mean((0.3*pvilmri2) + (0.5* ri2expertPrediction) + (0.2*gdpPrediction))

nm2expert <- expert_ratings %>% 
  filter(year==2022 & state=="New Mexico" & district==2) %>% 
  select(avg_rating)
nm2expertPrediction <- predict(districtexpertLM, nm2expert)
pvinm2 <- pvi %>% 
  filter(District=="New Mexico 2")
pvilmnm2 <- 50+((pvinm2$PVI_num)/2)
polls2022NM2 <- polls2022Dem %>% 
  filter(st_fips==35 & cd_fips==2)
nm2pollingprediction <-mean(predict(districtpollLM, polls2022NM2))
nm2Prediction <-mean((0.3*pvilmnm2) + (0.3* nm2expertPrediction) + (0.2*nm2pollingprediction) +(0.2*gdpPrediction))

nm2expert <- expert_ratings %>% 
  filter(year==2022 & state=="New Mexico" & district==2) %>% 
  select(avg_rating)
nm2expertPrediction <- predict(districtexpertLM, nm2expert)
pvinm2 <- pvi %>% 
  filter(District=="New Mexico 2")
pvilmnm2 <- 50+((pvinm2$PVI_num)/2)
polls2022NM2 <- polls2022Dem %>% 
  filter(st_fips==35 & cd_fips==2)
nm2pollingprediction <-mean(predict(districtpollLM, polls2022NM2))
nm2Prediction <-mean((0.3*pvilmnm2) + (0.3* nm2expertPrediction) + (0.2*nm2pollingprediction) +(0.2*gdpPrediction))

mi3expert <- expert_ratings %>% 
  filter(year==2022 & state=="Michigan" & district==3) %>% 
  select(avg_rating)
mi3expertPrediction <- predict(districtexpertLM, mi3expert)
pvimi3 <- pvi %>% 
  filter(District=="Michigan 3")
pvilmmi3 <- 50+((pvimi3$PVI_num)/2)
polls2022MI3 <- polls2022Dem %>% 
  filter(st_fips==26 & cd_fips==3)
mi3pollingprediction <-mean(predict(districtpollLM, polls2022MI3))
mi3Prediction <- mean((0.3*pvilmmi3) + (0.4* mi3expertPrediction) + (0.1*mi3pollingprediction) +(0.22*gdpPrediction))

md6expert <- expert_ratings %>% 
  filter(year==2022 & state=="Maryland" & district==6) %>% 
  select(avg_rating)
md6expertPrediction <- predict(districtexpertLM, md6expert)
pvimd6 <- pvi %>% 
  filter(District=="Maryland 6")
pvilmmd6 <- 50+((pvimd6$PVI_num)/2)
polls2022MD6 <- polls2022Dem %>% 
  filter(st_fips==24 & cd_fips==6)
md6pollingprediction <-mean(predict(districtpollLM, polls2022MD6))
md6Prediction <- mean((0.3*pvilmmd6) + (0.3* md6expertPrediction) + (0.2*md6pollingprediction) +(0.21*gdpPrediction))
```
```{r}
il17expert <- expert_ratings %>% 
  filter(year==2022 & state=="Illinois" & district==17) %>% 
  select(avg_rating)
il17expertPrediction <- predict(districtexpertLM, il17expert)
pviil17 <- pvi %>% 
  filter(District=="Illinois 17")
pvilmil17 <- 50+((pviil17$PVI_num)/2)
polls2022IL17 <- polls2022Dem %>% 
  filter(st_fips==17 & cd_fips==17)
il17pollingprediction <-mean(predict(districtpollLM, polls2022IL17))
il17Prediction <- mean((0.3*pvilmil17) + (0.5* il17expertPrediction) +(0.2*gdpPrediction))

or6expert <- expert_ratings %>% 
  filter(year==2022 & state=="Oregon" & district==6) %>% 
  select(avg_rating)
or6expertPrediction <- predict(districtexpertLM, or6expert)
pvior6 <- pvi %>% 
  filter(District=="Oregon 6")
pvilmor6 <- 50+((pvior6$PVI_num)/2)
polls2022OR6 <- polls2022Dem %>% 
  filter(st_fips==41 & cd_fips==6)
or6pollingprediction <-mean(predict(districtpollLM, polls2022OR6))
or6Prediction <- mean((0.3*pvilmor6) + (0.3* or6expertPrediction) + (0.2*or6pollingprediction) +(0.2*gdpPrediction))

nj7expert <- expert_ratings %>% 
  filter(year==2022 & state=="New Jersey" & district==7) %>% 
  select(avg_rating)
nj7expertPrediction <- predict(districtexpertLM, nj7expert)
pvinj7 <- pvi %>% 
  filter(District=="New Jersey 7")
pvilmnj7 <- 50+((pvinj7$PVI_num)/2)
polls2022NJ7 <- polls2022Dem %>% 
  filter(st_fips==34 & cd_fips==7)
nj7pollingprediction <-mean(predict(districtpollLM, polls2022NJ7))
nj7Prediction <- mean((0.3*pvilmnj7) + (0.3* nj7expertPrediction) + (0.2*nj7pollingprediction) +(0.2*gdpPrediction))

co8expert <- expert_ratings %>% 
  filter(year==2022 & state=="Colorado" & district==8) %>% 
  select(avg_rating)
co8expertPrediction <- predict(districtexpertLM, co8expert)
pvico8 <- pvi %>% 
  filter(District=="Colorado 8")
pvilmco8 <- 50+((pvico8$PVI_num)/2)
polls2022CO8 <- polls2022Dem %>% 
  filter(st_fips==8 & cd_fips==8)
co8pollingprediction <-mean(predict(districtpollLM, polls2022CO8))
co8Prediction <- mean((0.3*pvilmco8) + (0.3* co8expertPrediction) + (0.2*co8pollingprediction) +(0.2*gdpPrediction))

ny22expert <- expert_ratings %>% 
  filter(year==2022 & state=="New York" & district==22) %>% 
  select(avg_rating)
ny22expertPrediction <- predict(districtexpertLM, ny22expert)
pviny22 <- pvi %>% 
  filter(District=="New York 22")
pvilmny22 <- 50+((pviny22$PVI_num)/2)
polls2022NY22 <- polls2022Dem %>% 
  filter(st_fips==36 & cd_fips==22)
ny22pollingprediction <-mean(predict(districtpollLM, polls2022NY22))
ny22Prediction <- mean((0.3*pvilmny22) + (0.5* ny22expertPrediction) + (0.2*gdpPrediction))

me2expert <- expert_ratings %>% 
  filter(year==2022 & state=="Maine" & district==2) %>% 
  select(avg_rating)
me2expertPrediction <- predict(districtexpertLM, md6expert)
pvime2 <- pvi %>% 
  filter(District=="Maine 2")
pvilmme2 <- 50+((pvime2$PVI_num)/2)
polls2022ME2 <- polls2022Dem %>% 
  filter(st_fips==23 & cd_fips==2)
me2pollingprediction <-mean(predict(districtpollLM, polls2022ME2))
me2Prediction <- mean((0.3*pvilmme2) + (0.3* me2expertPrediction) + (0.2*me2pollingprediction) +(0.2*gdpPrediction))

nc13expert <- expert_ratings %>% 
  filter(year==2022 & state=="North Carolina" & district==13) %>% 
  select(avg_rating)
nc13expertPrediction <- predict(districtexpertLM, nc13expert)
pvinc13 <- pvi %>% 
  filter(District=="North Carolina 13")
pvilmnc13 <- 50+((pvinc13$PVI_num)/2)
polls2022NC13 <- polls2022Dem %>% 
  filter(st_fips==37 & cd_fips==13)
nc13pollingprediction <-mean(predict(districtpollLM, polls2022NC13))
nc13Prediction <- mean((0.3*pvilmnc13) + (0.3* nc13expertPrediction) + (0.2*nc13pollingprediction) +(0.2*gdpPrediction))

ny18expert <- expert_ratings %>% 
  filter(year==2022 & state=="New York" & district==18) %>% 
  select(avg_rating)
ny18expertPrediction <- predict(districtexpertLM, ny18expert)
pviny18 <- pvi %>% 
  filter(District=="New York 18")
pvilmny18 <- 50+((pviny18$PVI_num)/2)
polls2022NY18 <- polls2022Dem %>% 
  filter(st_fips==36 & cd_fips==18)
ny18pollingprediction <-mean(predict(districtpollLM, polls2022MD6))
ny18Prediction <- mean((0.3*pvilmny18) + (0.5* ny18expertPrediction) + (0.2*gdpPrediction))
```
```{r}
pa8expert <- expert_ratings %>% 
  filter(year==2022 & state=="Pennsylvania" & district==8) %>% 
  select(avg_rating)
pa8expertPrediction <- predict(districtexpertLM, pa8expert)
pvipa8 <- pvi %>% 
  filter(District=="Pennsylvania 8")
pvilmpa8 <- 50+((pvipa8$PVI_num)/2)
polls2022PA8 <- polls2022Dem %>% 
  filter(st_fips==42 & cd_fips==8)
pa8pollingprediction <-mean(predict(districtpollLM, polls2022PA8))
pa8Prediction <- mean((0.3*pvilmpa8) + (0.3* pa8expertPrediction) + (0.2*pa8pollingprediction) +(0.2*gdpPrediction))

nv3expert <- expert_ratings %>% 
  filter(year==2022 & state=="Nevada" & district==3) %>% 
  select(avg_rating)
nv3expertPrediction <- predict(districtexpertLM, nv3expert)
pvinv3 <- pvi %>% 
  filter(District=="Nevada 3")
pvilmnv3 <- 50+((pvinv3$PVI_num)/2)
polls2022NV3 <- polls2022Dem %>% 
  filter(st_fips==32 & cd_fips==3)
nv3pollingprediction <-mean(predict(districtpollLM, polls2022NV3))
nv3Prediction <- mean((0.3*pvilmnv3) + (0.3* nv3expertPrediction) + (0.2*nv3pollingprediction) +(0.2*gdpPrediction))

pa17expert <- expert_ratings %>% 
  filter(year==2022 & state=="Pennsylvania" & district==17) %>% 
  select(avg_rating)
pa17expertPrediction <- predict(districtexpertLM, pa17expert)
pvipa17 <- pvi %>% 
  filter(District=="Pennsylvania 17")
pvilmpa17 <- 50+((pvipa17$PVI_num)/2)
polls2022PA17 <- polls2022Dem %>% 
  filter(st_fips==42 & cd_fips==17)
pa17pollingprediction <-mean(predict(districtpollLM, polls2022NC13))
pa17Prediction <- mean((0.3*pvilmpa17) + (0.3* pa17expertPrediction) + (0.2*pa17pollingprediction) +(0.2*gdpPrediction))

ny3expert <- expert_ratings %>% 
  filter(year==2022 & state=="New York" & district==3) %>% 
  select(avg_rating)
ny3expertPrediction <- predict(districtexpertLM, ny3expert)
pviny3 <- pvi %>% 
  filter(District=="New York 3")
pvilmny3 <- 50+((pviny3$PVI_num)/2)
polls2022NY3 <- polls2022Dem %>% 
  filter(st_fips==36 & cd_fips==3)
ny3pollingprediction <-mean(predict(districtpollLM, polls2022NY3))
ny3Prediction <- mean((0.3*pvilmny3) + (0.5* ny3expertPrediction) +(0.22*gdpPrediction))

tx34expert <- expert_ratings %>% 
  filter(year==2022 & state=="Texas" & district==34) %>% 
  select(avg_rating)
tx34expertPrediction <- predict(districtexpertLM, tx34expert)
pvitx34 <- pvi %>% 
  filter(District=="Texas 34")
pvilmtx34 <- 50+((pvitx34$PVI_num)/2)
polls2022TX34 <- polls2022Dem %>% 
  filter(st_fips==48 & cd_fips==34 & candidate_name=="Vicente Gonzalez")
tx34pollingprediction <-mean(predict(districtpollLM, polls2022TX34))
tx34Prediction <- mean((0.3*pvilmtx34) + (0.3* tx34expertPrediction) + (0.2*tx34pollingprediction) +(0.2*gdpPrediction))

ny1expert <- expert_ratings %>% 
  filter(year==2022 & state=="New York" & district==1) %>% 
  select(avg_rating)
ny1expertPrediction <- predict(districtexpertLM, ny1expert)
pviny1 <- pvi %>% 
  filter(District=="New York 1")
pvilmny1 <- 50+((pviny1$PVI_num)/2)
polls2022NY1 <- polls2022Dem %>% 
  filter(st_fips==36 & cd_fips==1)
ny1pollingprediction <-mean(predict(districtpollLM, polls2022NY1))
ny1Prediction <- mean((0.3*pvilmny1) + (0.5* ny1expertPrediction) +(0.2*gdpPrediction))
```
```{r}
closedistricts <- matrix(c("AZ-2", "R", az2Prediction, "CA-22", "R", ca22Prediction, "CA-27", "R", ca27Prediction, "CO-8", "R", co8Prediction, "IA-3", "R", ia3Prediction, "IL-17", "R", il17Prediction, "KS-3", "R", ks3Prediction, "MD-6", "D", md6Prediction, "ME-2", "R", me2Prediction, "MI-10", "R", mi10Prediction, "MI-3", "D", mi3Prediction, "NC-13", "R", nc13Prediction, "NJ-7", "R", nj7Prediction, "NM-2", "R", nm2Prediction, "NV-3", "R", nv3Prediction, "NY-18", "R", ny18Prediction, "NY-19", "R", ny19Prediction, "NY-1", "R", ny1Prediction, "NY-22", "R", ny22Prediction, "NY-3", "D", ny3Prediction, "OR-5", "R", or5Prediction, "OR-6", "D", or6Prediction, "PA-17", "R", pa17Prediction, "PA-7", "R", pa7Prediction, "PA-8", "R", pa8Prediction, "RI-2", "D", ri2Prediction, "TX-15", "R", tx15Prediction, "TX-34", "D", tx34Prediction, "VA-2", "R", va2Prediction), ncol=3, byrow=TRUE)
colnames(closedistricts) <- c("District", "Winning Party", "Dem Voteshare (2-Party)")
stargazer(closedistricts, title="District Predictions of Close Races", type="text")
```
NOTE: REMEMBER TO EXPLAIN THAT IF THERE WERE NO POLLS THE WEIGHT FOR EXPERT WENT FROM 0.3 to 0.5